```{r executive, echo = FALSE}
assessmentyear <- as.numeric(format(Sys.Date(), "%Y")) - 1
area_long <- paste0(tolower(params$area), "ern ")
n_stocks <- xfun::numbers_to_words( length(get_groups(info_groups)))
```
# Executive summary{-}

## Stock{-}

```{asis executive-summary-stock, echo = TRUE}
This assessment reports the status of `r spp` (_`r spp.sci`_)
off the `r area_long` `r coast` coast
using data through `r assessmentyear`.
`r Spp` were modeled as `r n_stocks` `r ifelse(n_stocks > 1, "stocks", "stock")` and
this document contains summary information on the species and
detailed information for the `r area_long` stock.
It does not include catches from the Alaskan, Canadian, or Mexican populations and
assumes that these flanking populations do not contribute to the stock being assessed here.
```

## Landings{-}

The first known records of `r spp` landings date back to the early
```{asis catch-text-commfleetstructure, echo = TRUE}
```

## Data and assessment{-}
Replace text.

## Stock biomass{-}
Replace text.

## Recruitment{-}
Replace text.

## Exploitation status{-}
Replace text.

## Reference points{-}
Replace text.

## Management performance{-}
Replace text.

## Unresolved problems and major uncertainties{-}
Replace text.

## Decision table{-}
Replace text.

## Regional management considerations{-}
```{r results = "asis"}
sa4ss::read_child("regional-management-considerations.Rmd")
```

## Research and data needs{-}
```{r results = "asis"}
sa4ss::read_child("research-and-data-needs.Rmd")
```
