# Data

Descriptions of each data source included in the model (Figure \@ref(fig:data-plot))
and sources that were explored but not included
are provided below.

## Fishery-Dependent data

```{r render-catch, results = "asis"}
sa4ss::read_child(file.path("catch.Rmd"))
```

### \Glsentrylong{cpue}

```{r render-cpue-pacfin, results = "asis"}
sa4ss::read_child(file.path("commcpuepacfin.Rmd"))
```
```{r render-cpue, results = "asis", cache = TRUE, eval = grepl("North", params$area)}
sa4ss::read_child(file.path("commcpueor.Rmd"))
sa4ss::read_child(file.path("reccpuewa.Rmd"))
```
```{r render-cpueor, results = "asis", cache = FALSE, eval = grepl("North", params$area)}
sa4ss::read_child(file.path("reccpueor.Rmd"))
```
```{r render-cpueca, results = "asis", cache = FALSE}
sa4ss::read_child(file.path("reccpueca.Rmd"))
```

### Commercial length- and age-composition data
```{r render-commcomp, results = "asis"}
sa4ss::read_child("commcomp.Rmd")
```

### Recreational length- and age-composition data

```{r render-rec-comps-n, results = "asis", eval = grepl("North", params$area)}
sa4ss::read_child(file.path("rec-comps-north.Rmd"))
```
```{r render-rec-comps-s, results = "asis", eval = grepl("South", params$area)}
sa4ss::read_child(file.path("rec-comps-south.Rmd"))
```

### Discard data

```{r render-discards, results = "asis"}
sa4ss::read_child(file.path("discards.Rmd"))
```

### Unused fishery-dependent data

```{r render-24data-notused, results = "asis"}
sa4ss::read_child(file.path("24data-notused.Rmd"))
```

## Fishery-Independent data

### Survey indices

```{r render-surveyindices, results = "asis"}
sa4ss::read_child(file.path("surveyindex.Rmd"))
```

### Survey length- and age-composition data

```{r render-surveycomp, results = "asis"}
sa4ss::read_child(file.path("surveycomp.Rmd"))
```

### Unused fishery-independent data

```{r render-29data-notused, results = "asis"}
sa4ss::read_child(file.path("29data-notused.Rmd"))
```

```{r render-biology, results = "asis"}
sa4ss::read_child(file.path("22biology.Rmd"))
```
