# Data

Data comprise the foundational components of stock assessment models.
The decision to include or exclude particular data sources in an assessment model depends on many factors.
These factors often include, but are not limited to,
the way in which data were collected (e.g., measurement method and consistency);
the spatial and temporal coverage of the data;
the quantity of data available per desired sampling unit;
the representativeness of the data to inform the modeled processes of importance;
timing of when the data were provided;
limitations imposed by the Terms of Reference; and
the presence of an avenue for the inclusion of the data in the assessment model.
Attributes associated with a data source can change through time,
as can the applicability of the data source when different modeling approaches are explored (e.g., stock structure or time-varying processes).
Therefore, the specific data sources included or excluded from this assessment should not necessarily constrain the selection of data sources applicable to future stock assessments for `r spp`.
Even if a data source is not directly used in the stock assessment they can provide valuable insights into biology, fishery behavior, or localized dynamics.

Data from a wide range of programs were available for possible inclusion in the current assessment model.
Descriptions of each data source included in the model (Figure \@ref(fig:data-plot)) and sources that were explored but not included in the base model are provided below.
Data that were excluded from the base model were explicitly explored during the development of this stock assessment or have not changed since their past exploration in a previous `r spp` stock assessment.
In some cases, the inclusion of excluded data sources were explored through sensitivity analyses (see Section \@ref(assessment-model)).

## Fishery-Dependent data

```{r render-catch, results = "asis"}
sa4ss::read_child(file.path("catch.Rmd"))
```

### Catch per unit effort

```{r render-cpue-pacfin, results = "asis"}
sa4ss::read_child(file.path("commcpuepacfin.Rmd"))
```
```{r render-cpue, results = "asis", cache = TRUE, eval = grepl("North", params$area)}
sa4ss::read_child(file.path("commcpueor.Rmd"))
sa4ss::read_child(file.path("reccpuewa.Rmd"))
```
```{r render-cpueor, results = "asis", cache = FALSE, eval = grepl("North", params$area)}
sa4ss::read_child(file.path("reccpueor.Rmd"))
```
```{r render-cpueca, results = "asis", cache = FALSE}
sa4ss::read_child(file.path("reccpueca.Rmd"))
```

### Commercial length- and age-composition data
```{r render-commcomp, results = "asis"}
sa4ss::read_child("commcomp.Rmd")
```

### Recreational length- and age-composition data

```{r render-rec-comps-n, results = "asis", eval = grepl("North", params$area)}
sa4ss::read_child(file.path("rec-comps-north.Rmd"))
```
```{r render-rec-comps-s, results = "asis", eval = grepl("South", params$area)}
sa4ss::read_child(file.path("rec-comps-south.Rmd"))
```

### Discard data

```{r render-discards, results = "asis"}
sa4ss::read_child(file.path("discards.Rmd"))
```

### Unused fishery-dependent data

```{r render-24data-notused, results = "asis"}
sa4ss::read_child(file.path("24data-notused.Rmd"))
```

## Fishery-Independent data

### Survey indices

```{r render-surveyindices, results = "asis"}
sa4ss::read_child(file.path("surveyindex.Rmd"))
```

### Survey length- and age-composition data

```{r render-surveycomp, results = "asis"}
sa4ss::read_child(file.path("surveycomp.Rmd"))
```

### Unused fishery-independent data

```{r render-29data-notused, results = "asis"}
sa4ss::read_child(file.path("29data-notused.Rmd"))
```

```{r render-biology, results = "asis"}
sa4ss::read_child(file.path("22biology.Rmd"))
```
