## Biological data

### Natural mortality


### Maturation and fecundity


### Sex ratio


### Length-Weight relationship

The weight-length relationship for `r spp` was estimated outside the model 
using available biological data collected from the \Gls{s-wcgbt}. 
The weight-length relationship is based on the standard power function: $W = aL^b$
where W is weight in kilograms and L is fork length in centimeters. 

Hart (1967) reported the relationship between length and weight as $W = 0.000282406·L^{3.011}$. The length-weight relationship was estimated by Jagielo (1994) using available survey data and was fit to mean weight-at-length measured in the West Coast survey as $W = 0.000003953·L^{3.2149}$ for males and $W = 0.00000176 L^{3.3978}$ for females. 

Between 2003 and 2019, lengths and weights were measured for 

```{r, echo=FALSE, results='asis', opts.label = 'north'}
7,869 `r spp` on the \Gls{s-wcgbt} north 40 degrees 10 minutes N latitude. Of these samples, 4,978 were female,
and 2805 were male. 
```

```{r, echo=FALSE, results='asis', opts.label = 'south'}
5,547 `r spp` on the \Gls{s-wcgbt} south 40 degrees 10 minutes N latitude. Of these samples, 3,052 were female,
and 1,787 were male. 
```

Spatial differences were investigated by fitting an overall power 
relationship between length and weight across all coastwide samples, and then comparing the residuals 
across latitude, region, and depth using Tukey HSD pairwise multiple 
comparison tests. Residuals of the fit between length and weight showed 
significant differences among latitude (p-value < 0.001, as a continuous variable), and 
among regions north and south of 40 degrees 10 minutes N latitude (p-value < 0.001, as factors).  
The relationship between length and weight change with depth (p-value = 0.02, as a continuous variable), 
but not when applying similar depth categories (55 - 183, 183 - 400, and >400 m) as was used to expand composition data (p-value = 0.16), nor more refined depth categories 
(55 - 85, 85 - 110, 110 - 140, 140 - 183, and >183 m; p-value = 0.20). 

The parameters of the weight-length relationship were re-estimated using data from 
the \Gls{s-wcgbt}. New length and weight data from the survey for this assessment result in the 
following estimates for the weight-length relationships: 

```{r, echo=FALSE, results='asis', opts.label = 'north'}
$W=$`r format(lw_ests$North_NWFSC.Combo_F[1], scientific = TRUE)`$L^`r format(lw_ests$North_NWFSC.Combo_F[2], scientific = TRUE)` for females, and 
$W=$`r format(lw_ests$North_NWFSC.Combo_M[1], scientific = TRUE)`$L^`r format(lw_ests$North_NWFSC.Combo_M[2], scientific = TRUE)` for males 
```

```{r, echo=FALSE, results='asis', opts.label = 'south'}
$W=$`r format(lw_ests$South_NWFSC.Combo_F[1], scientific = TRUE)`$L^`r format(lw_ests$South_NWFSC.Combo_F[2], scientific = TRUE)` for females, and 
$W=$`r format(lw_ests$South_NWFSC.Combo_M[1], scientific = TRUE)`$L^`r format(lw_ests$South_NWFSC.Combo_M[2], scientific = TRUE)` for males 
```

(Figure \ref{fig:len-weight}). These relationships are very similar to those used for the previous assessment (@Haltuch_lingcod_2017).


### Growth (length-at-age)

A model based change-point analysis [@kapur2020]
was used to identify a biologically relevant stock boundary using size-at-age data
from the \gls{s-wcgbt} and `r get_fleet("Lam", col="label_long")` [@lam2021geographic].
A generalized additive model was fit to
observed `r spp` lengths of a single age as the response variable.
Predictor variables included a smoother for latitude.
Each age-sex combination was analyzed separately.
The first derivative was taken from the fitted spline
to detect the latitude at which differences in size-at-age were most pronounced
(i.e., the maximum absolute value) and
statistically significant
(i.e., where the confidence interval does not include 0).
The resulting latitude was rounded to the nearest integer
as there were no detectable differences when half-degrees were used.
77.8\% of significant age-sex combinations detected a break between latitudes
$38^\circ 00^\prime$ and $40^\circ 00^\prime$ N
(Figure \@ref(fig:Lam-kapurage7latitude)).
This range is in agreement with the genetic break point identified for
`r spp` by Longo et al. [-@longo2020strong].

`r Spp` display sexually dimorphic growth.
Females grow faster than and reach larger sizes than males.
Jagielo (1994) estimated growth using a fixed length at age 1 of 30 cm,
and estimated $L_{\infty}$ for males of 93.21 cm and females of 131.05 cm,
and $k$ of 0.1694 for males and 0.1137 for females.
He also found that the average length for young-of-the-year (age-0)
`r spp` was 11.99 cm and for age 2 was 48.1 cm for Washington samples.
Additionally, growth trajectories diverge considerably by sex after age 3
because female `r spp` tend to grow faster and live longer than male `r spp`.
Male `r spp` mature at age 3.

Estimates of growth parameters were investigated and starting values for model inputs were updated using the \Gls{s-wcgbt} data. Spatial differences were investigated by fitting an overall von Bertalanffy relationship between age and length across all coastwide samples, and then comparing the residuals across latitude and depth using Tukey HSD pairwise multiple comparison tests. Residuals of the fit between age and length showed significant differences among latitude (p-value < 0.001, as a continuous variable), and among regions north and south of 40 degrees 10 minutes N latitude (p-value < 0.001, as factors). `r Spp` 
growth faster and attained a larger size in north of 40 degrees 10 minutes N latitude. 
The relationship between age and length changed with depth (p-value = 0.02, as a continuous 
variable), and unlike with the length-weight relationship, age and length fits varied by
depth bins (p-value < 0.001). When applying similar depth categories (55 - 183, 183 - 400, and >400 m) as was used to expand composition data, patterns were not statistically distinguishable between shallow (55 - 183 m) and deep (>400 m) depths (p-value = 0.62), and mid (183-400 m) and deep depths (p-value = 0.24). When using more refined depth categories (55 - 85, 85 - 110, 110 - 140, 140 - 183, and >183 m), 
patterns were nearly not statistically distinguishable between shallow (<85 m) and 
mid-shallow (85-110 m) depths (p-value = 0.043), and were not statistically distinguishable 
between mid-deep (140-183 m) and deep (>183 m) depths (p-value = 0.84).

Externally estimated von Bertalanffy growth parameters for `r spp` using the 2003-2019 \Gls{s-wcgbt} data are:

```{r, echo=FALSE, results='asis', opts.label = 'north'}
$k$ = `r round(la_ests$North_NWFSC.Combo_F[2],3)` and  $L_{\infty}$ = `r round(la_ests$North_NWFSC.Combo_F[1],3)` for females, and $k$= `r  round(la_ests$North_NWFSC.Combo_M[2],3)` and  $L_{\infty}$ = `r round(la_ests$North_NWFSC.Combo_M[1],3)` for males. 

These estimates are from 5,145 age and length samples, of which 3,290 are female, and 1,795 are male.
```

```{r, echo=FALSE, results='asis', opts.label = 'south'}
$k$ = `r round(la_ests$South_NWFSC.Combo_F[2],3)` and  $L_{\infty}$ = `r round(la_ests$South_NWFSC.Combo_F[1],3)` for females, and $k$= `r  round(la_ests$South_NWFSC.Combo_M[2],3)` and  $L_{\infty}$ = `r round(la_ests$South_NWFSC.Combo_M[1],3)` for males. 

These estimates are from 3,910 age and length samples, of which 2,178 are female, and 1,228 are male.
```


Internally estimated growth curves are shown in ??

[NEED TO PROVIDE INTERNALLY ESTIMATED GROWTH CURVE FIGURE]


### Ageing precision and bias

`r Spp` are aged using dorsal fin rays,
which has been found to have the highest
accuracy,
readability,
and minimal between-reader bias when compared to other ageing structures
[e.g., @chiltonAgeDeterm; @cass1983first; Claiborne et al. 2016].
However, recent studies suggest that surface reads from otoliths may be
comparable in terms of accuracy and readability.
For  this assessment, `r spp` samples from
fishery-dependent and -independent sources were aged using the fin ray method.

During the age reading process,
the first and second annuli can be re-absorbed as the fish ages,
obscuring early annulus rings and leading to error by under-ageing.
However, error can be minimized using known mean annular radii measurements
for the first, second, and third annuli, as established by
Beamish and Chilton [-@beamish1977age] and
later validated by
McFarlane and King [-@mcfarlane2001validity].

For this assessment,
between-reader ageing error was determined using the nwfscAgeingError package [@nwfscAgeingError2008],
which is publicly available at https://github.com/nwfsc-assess/nwfscAgeingError.
This package implements the Punt et al. [-@punt2008quantifying] model.
It calculates the likelihood of model parameters given an observed data set
that includes age reads provided by multiple readers for a set of ageing structures.
For each reader, two sets of parameters are estimated that define
the standard deviation and bias of the reads provided by that reader.
The set of parameters that best describes the standard deviation and bias between age readers
is determined with a step-wise model selection function and compared using AIC.
