# Model

## Previous assessments and reviews

### History of modeling approaches

Since 1986,
there have been nine assessments of `r spp` covering at least part of the U.S. west coast.
The first assessment was performed by Adams [-@pfmclingcod1986] and
consisted of a yield per recruit analysis.
Each of the subsequent assessments utilized an age-structured model,
though the structure and form has changed with time.

The second assessment, conducted by Jagielo [-@jagielo1994assessment],
was conducted using an earlier version of Stock Synthesis [@methot_stock_2013] and
focused on the northern area.
Data were limited to the region between
Cape Falcon in Northern Oregon and
49\textdegree 00\textquotesingle N latitude
(off of southwest Vancouver Island in British Columbia).
This included \Gls{psmfc} areas 3A, 3B, and 3C, inclusive of Canada.
Two fleets were modeled, trawl and recreational, from 1979-1993,
two \gls{cpue} time series were included, \gls{s-tri} and trawl, and
length- and age-composition data were used to estimate selectivity.
The final spawning output was estimated to be approximately
20\% of pristine levels, and
catch recommendations ranged between 2500 and 3000 mt
based on fishing mortality levels of 20\% and 40\%.

The third assessment was conducted in 1997 [@jagielo1997assessment] and
expanded the area included south to Cape Blanco (42\textdegree 50\textquotesingle N latitude).
The estimated fraction unfished was below 0.10,
which led to the Council implementing substantial coastwide reductions in harvest and
recommending that the southern portion of the stock also be assessed.
Two years later, Adams et al. [-@pfmclingcod1999] conducted a length-based, age-structured population model
implemented in \gls{admb} [@fournier1996] for the southern area,
including Eureka, Monterey, and Conception \gls{inpfc} areas.
Since then, `r spp` assessments have covered the entire U.S. west coast but
been broken into two assessments using various spatial delineations.

In 2000,
Jagielo et al. [-@jagielo2000assessment] fit data to \gls{admb} models
using the same spatial delineation but removing data from Canadian waters.
Both stocks showed increasing trends in their abundance and
new ageing methods suggested the stocks were younger and more productive.
The populations were assessed again in 2003,
this time using Coleraine [@pfmclingcod2003].
In 2005, Jagielo et al. [-@pfmclingcod2005] switched back to Stock Synthesis,
which was then at version 2 of the code base.
Estimates suggested that the northern stock had recovered substantially
from a low point in the 1990s and was at 0.87 fraction unfished,
while the southern area was not estimated to have recovered and was at 0.24 fraction unfished,
with a 0.64 coastwide fraction unfished.

The 2009 stock assessment, which used Stock Synthesis 2,
divided the northern (Washington and Oregon) and southern (California) stocks
at the Oregon-California state line [@hamel2009lingcod].
The northern and southern models were made as equivalent as possible
by keeping fixed and estimated parameters largely the same for the two assessments.
Natural mortality was fixed at 0.18 for females and 0.32 for males in both assessments,
while steepness was fixed at 0.8.
Age data were removed because of issues with outliers and possible aging bias.
The estimate of fraction unfished at the start of 2009 was
0.619 for the northern area and 0.737 for the southern area,
indicating the stocks had recovered.
For the northern stock,
the axis of uncertainty for the decision table provided to managers was $M$.
The low, base, and high values of $M_{female}$ were 0.16, 0.18, and 0.20.
The low, base, and high values of $M_{male}$ were 0.285, 0.320, and 0.355.
For the southern stock,
the lower axis of uncertainty was for the he exclusion of the dockside recreational \gls{cpue} index and
the higher axis of uncertainty was the inclusion of age data.

The 2017 assessment [@haltuch2019lingcod] was conducted using Stock Synthesis and
matched the spatial structure used for 2009 [@hamel2009lingcod].
The assessment updated the existing data sources, as per normal protocol, and
also included the following changes:

- expansion of the time period of the assessments back to 1889,
- separation of commercial fleets into TW and FG,
- separation of recreational fleets in the northern stock to state-specific fleets,
- addition of numerous fishery-dependent \gls{cpue} indices and the \gls{s-hkl} index
- updated prior on natural mortality
- updated biological parameters for maturity and length-weight relationship
- updated ageing uncertainty
- included some age data as marginal ages instead of ages conditioned on length

The estimated scale of the population was sensitive to the inclusion of age data for both stocks.
These estimates of status remained the same regardless of whether or not the model was fit to age data.
The northern stock was estimated to be above the target reference point of 
0.40 fraction unfished.
The southern stock was estimated to be below the target reference point of
0.40 fraction unfished at 0.321.

In 2019, a catch-only projection was conducted.
This update assessment included observed catches for 2017 and 2018 in the forecast calculations.
Expected catches for 2019 and 2020 were also included in the forecast calculations.
The results provided updated catch limits for management.

### Most recent STAR panel and SSC recommendations{#STAR}

```{r render-STARpanelRecs, results = "asis"}
sa4ss::read_child(file.path("STARpanelRecs.Rmd"))
```

### Response to Groundfish Subcommittee recommendations



## Model structure and assumptions

```{r render-model-changes, results = "asis"}
sa4ss::read_child("model-changes.Rmd")
```

### General model specifications

```{r render-model-specification, results = "asis"}
sa4ss::read_child("model-specifications.Rmd")
```
```{r render-model-selectivity, results = "asis"}
sa4ss::read_child("model-selectivity.Rmd")
```

### Model parameters {#sec-model-parameters}

```{r render-model-parameters, results = "asis"}
sa4ss::read_child("model-parameters.Rmd")
```

### Base model selection {#sec-model-selection}

```{r render-model-selection, results = "asis"}
sa4ss::read_child("model-selection.Rmd")
```

### Base model results

```{r render-model-results, results = "asis"}
sa4ss::read_child("model-results.Rmd")
```

### Model diagnostics

#### Convergence

```{r render-model-jitter, results = "asis"}
sa4ss::read_child(file.path(paste0(params$model, "_jitter_0.05"), "model-results-jitter.md"))
```

#### Sensitivity Analyses

```{r render-model-sensitivities, results = "asis"}
sa4ss::read_child("model-sensitivities.Rmd")
```

#### Likelihood Profiles

```{r render-model-profile, results = "asis"}
sa4ss::read_child("model-profile.Rmd")
```

#### Retrospective Analysis

A five-year retrospective analysis was conducted by successively removing years of data
starting with the most recent year.
For the removal of the most recent year of data there were no changes to the model
trajectory or estimates of fraction unfished
(Figures \@ref(fig:RetroSsb) and \@ref(fig:RetroFractionunfished)).
```{asis, opts.label = "north"}
Peeling off more than one year of data led to a retrospective pattern with respect
to the estimated scale of the population but not current status.
```
```{asis, opts.label = "south"}
Removing five years of data led to a different historical time series for the stock,
one that indicated much higher productivity.
Regardless, the estimate of the current spawning stock biomass remained largely
consistent with the estimates from the base model.
```
Given time constraints, each of these models were not tuned, i.e.,
data weighting was not performed in an iterative fashion and bias adjustment
was not conducted, which could impact the model results.

### Evaluation of uncertainty

<!-- text below poached from Dover https://github.com/chantelwetzel-noaa/dover_sole_2021/ -->
The model estimated uncertainty around the `r model$endyr+1` spawning biomass 
was $\sigma$ = `r round(as.numeric(model$Pstar_sigma),2)` and the uncertainty around 
the OFL was $\sigma$ = `r round(as.numeric(model$OFL_sigma), 2)`. This is an 
underestimate of overall uncertainty because there is no explicit incorporation 
of model structural uncertainty.

### Comparison of north and south models

```{r render-model-compareareas, results = "asis"}
sa4ss::read_child("model-north-vs-south.Rmd")
```
