\clearpage
<!--
to do onboarding sa4ss - move this to sa4ss.sty so everyone's figures hold their order
https://stackoverflow.com/questions/29696172/how-to-hold-figure-position-with-figure-caption-in-pdf-output-of-knitr
-->
\floatplacement{table}{H}
# Tables

```{r table-catch, results = "asis"}
sa4ss::read_child(string_switchletter(
  file.path("..", "tables", "table-catchbystate-s-.tex"),
  params$area
))
```

```{r table-management-refpoints, results = "asis"}
management_oflabcacl <- utils::read.csv(file.path("..", "tables", "management-oflabcacl.csv"))
management_oflabcacl %>%
  dplyr::filter(area == params$area) %>%
  dplyr::select(-area) %>%
  dplyr::left_join(
    x = .,
    y = model[["catch"]] %>%
      dplyr::group_by(Yr) %>%
      dplyr::summarize(Observed = sum(Obs, na.rm = TRUE), Expected = sum(kill_bio, na.rm = TRUE), .groups = "keep") %>%
      dplyr::ungroup(),
    by = c(Year = "Yr")
  ) %>%
  dplyr::mutate_at(2:NCOL(.), ~ sprintf("%.2f", .x)) %>%
  kableExtra::kbl(
    longtable = FALSE, booktabs = TRUE, format = "latex",
    caption = paste0(
      "Recent trends in observed landings and expected dead biomass (mt) relative to management guidelines (\\glsentrylong{ofl}, \\glsentryshort{ofl}; \\glsentrylong{abc}, \\glsentryshort{abc}; \\glsentrylong{acl}, \\glsentryshort{acl}). Expected dead biomass represents the total landings plus the model-estimated dead discard biomass.",
      " ", text_wcgop, " ",
      "Additionally, management in 2011 and 2012 was based on a break at 42\\textdegree00\\textquotesingle N versus all other years used \\CapeM."
    ),
    label = "management-refpoints"
  ) %>%
  kableExtra::add_header_above(c(" ", "Management" = 3, "Landings" = 2)) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"))
```

```{r, cpue-tables-north, results = "asis", eval = grepl("North", params$area)}
ignore <- mapply(sa4ss::read_child, "../tables/cpue-commercialfixed-gear-filter.tex")
ignore <- mapply(sa4ss::read_child, "../tables/reccpuewa-filtersummary.tex")
ignore <- mapply(sa4ss::read_child, "../tables/cpue-recreationalOregon-filter.tex")
```

```{asis, opts.label="south"}
\begin{table}

\caption{\label{tab:data-filter-cpfvonboard}Data filtering for the California \glsentrylong{cpfv} onboard survey of lingcod in the southern California recreational fishery.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{15em}c>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}}
\toprule
Filter & Description & Trip & Positive Trips & \% drifts retained\\
\midrule
\cellcolor{gray!6}{All} & \cellcolor{gray!6}{Download from SQL; identifiable errors filtered} & \cellcolor{gray!6}{41168} & \cellcolor{gray!6}{1866} & \cellcolor{gray!6}{5\%}\\
Fishery closed & Removed samples when target fish fishery closed & 33224 & 1834 & 6\%\\
\cellcolor{gray!6}{Ocean only} & \cellcolor{gray!6}{Removed samples from major bays} & \cellcolor{gray!6}{33029} & \cellcolor{gray!6}{1834} & \cellcolor{gray!6}{6\%}\\
Catch & Removed samples with zero catch of any species & 30469 & 1834 & 6\%\\
\cellcolor{gray!6}{Depth} & \cellcolor{gray!6}{Removed samples in less than max depth of species} & \cellcolor{gray!6}{29858} & \cellcolor{gray!6}{1817} & \cellcolor{gray!6}{6\%}\\
\addlinespace
Time fished & Removed upper two percent of time fished & 29252 & 1802 & 6\%\\
\cellcolor{gray!6}{Percent groundfish in samples} & \cellcolor{gray!6}{Removed samples with fewer groundfish than when the target observed} & \cellcolor{gray!6}{14664} & \cellcolor{gray!6}{1718} & \cellcolor{gray!6}{12\%}\\
Another area gfish filter & Removed samples & 9043 & 1469 & 16\%\\
\bottomrule
\end{tabular}
\end{table}
```


<!-- Unused fishery-dependent data -->
```{r, cpue-tables, results = "asis", eval = grepl("North", params$area)}
ignore <- mapply(sa4ss::read_child, "../tables/fi-index-ormarres-N.tex")
ignore <- mapply(sa4ss::read_child, "../tables/fi-index-ormarres-mr.tex")
```

<!-- Hook and line index -->
```{asis, opts.label = "south"}
\begin{table}
\caption{\label{tab:tab-depth-nwfschl}Positive samples of lingcod in the \glsentrylong{s-hkl} by depth (fm).}
\centering
\begin{tabular}[t]{lrrl}
\toprule
Year & Positive Samples & Samples & Percent Positive\\
\midrule
\cellcolor{gray!6}{(0,50]} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{2\%}\\
(50,75] & 86 & 724 & 12\%\\
\cellcolor{gray!6}{(75,100]} & \cellcolor{gray!6}{226} & \cellcolor{gray!6}{2383} & \cellcolor{gray!6}{9\%}\\
(100,125] & 123 & 1620 & 8\%\\
\cellcolor{gray!6}{(125,150]} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{1121} & \cellcolor{gray!6}{9\%}\\
\addlinespace
(150,175] & 98 & 982 & 10\%\\
\cellcolor{gray!6}{(175,200]} & \cellcolor{gray!6}{20} & \cellcolor{gray!6}{268} & \cellcolor{gray!6}{7\%}\\
(200,230] & 14 & 97 & 14\%\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{\label{tab:tab-depthsite-nwfschl}Samples of lingcod in the \glsentrylong{s-hkl} by area and depth bins (ft).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllllll}
\toprule
Area name & (125,150] & (175,200] & (200,230] & (0,50] & (50,75] & (75,100] & (100,125] & (150,175]\\
\midrule
\cellcolor{gray!6}{Fourteen Mile Bank} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
107 and 118 Banks &  & 5\% & 0\% &  &  &  &  & \\
\cellcolor{gray!6}{43 Fathom Bank} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{3\%} & \cellcolor{gray!6}{10\%} & \cellcolor{gray!6}{}\\
Anacapa Island & 18\% & 0\% &  &  & 0\% & 4\% & 4\% & 9\%\\
\cellcolor{gray!6}{Catalina Island} & \cellcolor{gray!6}{10\%} & \cellcolor{gray!6}{11\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{11\%}\\
\addlinespace
Central Coast &  &  &  &  &  & 2\% & 0\% & \\
\cellcolor{gray!6}{Cherry Bank} & \cellcolor{gray!6}{10\%} & \cellcolor{gray!6}{5\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{9\%} & \cellcolor{gray!6}{10\%} & \cellcolor{gray!6}{}\\
Cortez Bank & 4\% &  &  & 12\% & 6\% & 5\% & 3\% & 7\%\\
\cellcolor{gray!6}{Garrett Bank} & \cellcolor{gray!6}{6\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{}\\
Harrison Reef & 0\% &  &  &  &  & 2\% & 1\% & \\
\addlinespace
\cellcolor{gray!6}{Hidden Reef} & \cellcolor{gray!6}{25\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{7\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{9\%}\\
Kidney Bank & 11\% &  &  &  &  &  & 12\% & 0\%\\
\cellcolor{gray!6}{Nine Mile Bank} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{0\%}\\
Osborn Bank &  &  &  & 0\% & 15\% & 32\% &  & 24\%\\
\cellcolor{gray!6}{Point Conception/Arguello} & \cellcolor{gray!6}{14\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{11\%} & \cellcolor{gray!6}{11\%} & \cellcolor{gray!6}{3\%}\\
\addlinespace
Potato Bank & 4\% &  &  &  &  & 20\% & 8\% & \\
\cellcolor{gray!6}{San Clemente Island} & \cellcolor{gray!6}{8\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{6\%} & \cellcolor{gray!6}{1\%} & \cellcolor{gray!6}{5\%}\\
San Miguel Island & 10\% &  &  &  & 41\% & 22\% & 10\% & \\
\cellcolor{gray!6}{San Nicolas Island East} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{17\%} & \cellcolor{gray!6}{25\%} & \cellcolor{gray!6}{33\%} & \cellcolor{gray!6}{5\%}\\
San Nicolas Island West & 40\% & 0\% &  &  & 5\% & 11\% & 20\% & 5\%\\
\addlinespace
\cellcolor{gray!6}{San Pedro Bay} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{4\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
Santa Barbara &  &  &  & 1\% & 17\% & 5\% &  & \\
\cellcolor{gray!6}{Santa Barbara Channel} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{2\%} & \cellcolor{gray!6}{13\%}\\
Santa Barbara Island & 8\% & 8\% & 0\% & 4\% & 0\% & 12\% & 15\% & 19\%\\
\cellcolor{gray!6}{Santa Cruz Island} & \cellcolor{gray!6}{33\%} & \cellcolor{gray!6}{15\%} & \cellcolor{gray!6}{20\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{6\%} & \cellcolor{gray!6}{9\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{17\%}\\
\addlinespace
Santa Monica Bay & 1\% &  &  &  &  & 1\% & 0\% & \\
\cellcolor{gray!6}{Santa Rosa Flats} & \cellcolor{gray!6}{11\%} & \cellcolor{gray!6}{6\%} & \cellcolor{gray!6}{15\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{9\%} & \cellcolor{gray!6}{11\%}\\
Santa Rosa Island &  &  &  &  & 18\% & 19\% & 0\% & \\
\cellcolor{gray!6}{Sixty Mile Bank} & \cellcolor{gray!6}{2\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{2\%} & \cellcolor{gray!6}{0\%}\\
South Coast &  &  &  & 0\% & 3\% & 6\% &  & \\
\addlinespace
\cellcolor{gray!6}{Tanner Bank} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{7\%} & \cellcolor{gray!6}{0\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{3\%} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{0\%}\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}
\caption{\label{tab:tab-year-nwfschl}Samples of lingcod in the \glsentrylong{s-hkl} by year.}
\centering
\begin{tabular}[t]{lrrl}
\toprule
Year & Positive Samples & Samples & Percent Positive\\
\midrule
\cellcolor{gray!6}{2004} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{11\%}\\
2005 & 27 & 307 & 9\%\\
\cellcolor{gray!6}{2006} & \cellcolor{gray!6}{17} & \cellcolor{gray!6}{303} & \cellcolor{gray!6}{6\%}\\
2007 & 27 & 335 & 8\%\\
\cellcolor{gray!6}{2008} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{412} & \cellcolor{gray!6}{3\%}\\
\addlinespace
2009 & 16 & 405 & 4\%\\
\cellcolor{gray!6}{2010} & \cellcolor{gray!6}{11} & \cellcolor{gray!6}{414} & \cellcolor{gray!6}{3\%}\\
2011 & 30 & 393 & 8\%\\
\cellcolor{gray!6}{2012} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{414} & \cellcolor{gray!6}{13\%}\\
2013 & 62 & 409 & 15\%\\
\addlinespace
\cellcolor{gray!6}{2014} & \cellcolor{gray!6}{67} & \cellcolor{gray!6}{530} & \cellcolor{gray!6}{13\%}\\
2015 & 75 & 615 & 12\%\\
\cellcolor{gray!6}{2016} & \cellcolor{gray!6}{77} & \cellcolor{gray!6}{623} & \cellcolor{gray!6}{12\%}\\
2017 & 69 & 652 & 11\%\\
\cellcolor{gray!6}{2018} & \cellcolor{gray!6}{64} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{10\%}\\
\addlinespace
2019 & 37 & 660 & 6\%\\
\bottomrule
\end{tabular}
\end{table}
```


<!-- Sample size tables -->
```{r, comp-sample-size-tables, results = "asis"}

sa4ss::read_child(filein = file.path("..", "tables", paste0("length_samps_", params$area, ".tex")))

sa4ss::read_child(filein = file.path("..", "tables", paste0("age_samps_", params$area, ".tex")))
```

<!-- Sample size tables for commercial by state -->
```{r, comp-sample-size-tables-commbyState, results = "asis", eval = grepl("North", params$area)}

sa4ss::read_child(filein = file.path("..", "tables", paste0("length_samps_comm_byState_", params$area, ".tex")))

sa4ss::read_child(filein = file.path("..", "tables", paste0("age_samps_comm_byState_", params$area, ".tex")))
```

<!-- s-ccfrp tables -->
\begin{table}
\caption{(\#tab:tab-region-ccfrp)\glsfirst{s-ccfrp} samples of `r spp` by subregion used to generate an index of abundance.}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Year & Samples & Positive Samples & \% Positive\\
\midrule
\cellcolor{gray!6}{South Cape Mendocino} & \cellcolor{gray!6}{131} & \cellcolor{gray!6}{289} & \cellcolor{gray!6}{45\%}\\
Ten Mile & 139 & 297 & 47\%\\
\cellcolor{gray!6}{Stewarts Point} & \cellcolor{gray!6}{127} & \cellcolor{gray!6}{293} & \cellcolor{gray!6}{43\%}\\
Bodega Head & 139 & 275 & 51\%\\
\cellcolor{gray!6}{Ano Nuevo} & \cellcolor{gray!6}{701} & \cellcolor{gray!6}{1879} & \cellcolor{gray!6}{37\%}\\
\addlinespace
Point Lobos & 553 & 1369 & 40\%\\
\cellcolor{gray!6}{Piedras Blancas} & \cellcolor{gray!6}{384} & \cellcolor{gray!6}{953} & \cellcolor{gray!6}{40\%}\\
Point Buchon & 535 & 1324 & 40\%\\
\cellcolor{gray!6}{Anacapa Island} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{52} & \cellcolor{gray!6}{6\%}\\
Carrington Point & 93 & 182 & 51\%\\
\addlinespace
\cellcolor{gray!6}{South La Jolla} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{18\%}\\
\bottomrule
\end{tabular}
\end{table}

```{asis, opts.label = 'south', echo = TRUE}
\begin{table}
\caption{(\#tab:tab-year-ccfrp)Samples of `r spp` in the \glsfirst{s-ccfrp} data by year.}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Year & Samples & Positive Samples & \% Positive\\
\midrule
\cellcolor{gray!6}{2007} & \cellcolor{gray!6}{87} & \cellcolor{gray!6}{552} & \cellcolor{gray!6}{16\%}\\
2008 & 134 & 564 & 24\%\\
\cellcolor{gray!6}{2009} & \cellcolor{gray!6}{94} & \cellcolor{gray!6}{370} & \cellcolor{gray!6}{25\%}\\
2010 & 142 & 420 & 34\%\\
\cellcolor{gray!6}{2011} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{374} & \cellcolor{gray!6}{45\%}\\
\addlinespace
2012 & 237 & 397 & 60\%\\
\cellcolor{gray!6}{2013} & \cellcolor{gray!6}{201} & \cellcolor{gray!6}{428} & \cellcolor{gray!6}{47\%}\\
2014 & 262 & 449 & 58\%\\
\cellcolor{gray!6}{2015} & \cellcolor{gray!6}{135} & \cellcolor{gray!6}{224} & \cellcolor{gray!6}{60\%}\\
2016 & 240 & 429 & 56\%\\
\addlinespace
\cellcolor{gray!6}{2017} & \cellcolor{gray!6}{304} & \cellcolor{gray!6}{590} & \cellcolor{gray!6}{52\%}\\
2018 & 332 & 700 & 47\%\\
\cellcolor{gray!6}{2019} & \cellcolor{gray!6}{279} & \cellcolor{gray!6}{740} & \cellcolor{gray!6}{38\%}\\
2020 & 197 & 726 & 27\%\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{(\#tab:tab-depth-ccfrp)Positive samples of `r spp` in the \glsfirst{s-ccfrp} data by depth (fm) bin.}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Year & Samples & Positive Samples & \% Positive\\
\midrule
\cellcolor{gray!6}{(0,10]} & \cellcolor{gray!6}{589} & \cellcolor{gray!6}{1809} & \cellcolor{gray!6}{33\%}\\
(10,15] & 1215 & 2942 & 41\%\\
\cellcolor{gray!6}{(15,20]} & \cellcolor{gray!6}{834} & \cellcolor{gray!6}{1827} & \cellcolor{gray!6}{46\%}\\
(20,30] & 176 & 385 & 46\%\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{(\#tab:tab-model-select-ccfrp)Model selection for the \glsfirst{s-ccfrp} index was performed using \glsfirst{aic} to select factors that explained the data in the most parsimonious manner.}
\centering
\begin{tabular}[t]{lrr}
\toprule
Model & Binomial $\Delta$AIC & Lognormal $\Delta$AIC\\
\midrule
\cellcolor{gray!6}{1} & \cellcolor{gray!6}{873.41} & \cellcolor{gray!6}{775.69}\\
YEAR + AREA & 237.89 & 160.63\\
\cellcolor{gray!6}{YEAR + AREA + SITE} & \cellcolor{gray!6}{55.57} & \cellcolor{gray!6}{46.76}\\
YEAR + AREA + SITE + DEPTH bin & 0.00 & 0.00\\
\cellcolor{gray!6}{YEAR + SITE + DEPTH bin} & \cellcolor{gray!6}{83.23} & \cellcolor{gray!6}{403.90}\\
\addlinespace
YEAR + DEPTH bin & 241.15 & 497.94\\
\cellcolor{gray!6}{YEAR + AREA + DEPTH bin} & \cellcolor{gray!6}{151.37} & \cellcolor{gray!6}{97.41}\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{(\#tab:tab-index-ccfrp)Standardized index for the \glsfirst{s-ccfrp} survey index with log-scale standard errors (SE) and 95\% highest posterior density (HPD) intervals for `r spp`.}
\centering
\begin{tabular}[t]{rrrrr}
\toprule
Year & Mean & log SE & lower HPD & upper HPD\\
\midrule
\cellcolor{gray!6}{2007} & \cellcolor{gray!6}{0.24} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{0.16} & \cellcolor{gray!6}{0.33}\\
2008 & 0.30 & 0.16 & 0.21 & 0.40\\
\cellcolor{gray!6}{2009} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{0.17} & \cellcolor{gray!6}{0.25} & \cellcolor{gray!6}{0.49}\\
2010 & 0.45 & 0.14 & 0.33 & 0.58\\
\cellcolor{gray!6}{2011} & \cellcolor{gray!6}{0.63} & \cellcolor{gray!6}{0.13} & \cellcolor{gray!6}{0.49} & \cellcolor{gray!6}{0.79}\\
\addlinespace
2012 & 0.85 & 0.10 & 0.69 & 1.03\\
\cellcolor{gray!6}{2013} & \cellcolor{gray!6}{0.77} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{0.60} & \cellcolor{gray!6}{0.97}\\
2014 & 1.08 & 0.10 & 0.87 & 1.30\\
\cellcolor{gray!6}{2015} & \cellcolor{gray!6}{1.19} & \cellcolor{gray!6}{0.11} & \cellcolor{gray!6}{0.94} & \cellcolor{gray!6}{1.46}\\
2016 & 0.92 & 0.11 & 0.74 & 1.13\\
\addlinespace
\cellcolor{gray!6}{2017} & \cellcolor{gray!6}{0.78} & \cellcolor{gray!6}{0.10} & \cellcolor{gray!6}{0.63} & \cellcolor{gray!6}{0.95}\\
2018 & 0.56 & 0.11 & 0.44 & 0.68\\
\cellcolor{gray!6}{2019} & \cellcolor{gray!6}{0.38} & \cellcolor{gray!6}{0.13} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{0.49}\\
2020 & 0.43 & 0.15 & 0.31 & 0.56\\
\bottomrule
\end{tabular}
\end{table}
```


<!-- ====================================================================== -->
<!-- 30model tables -->
<!-- ====================================================================== -->
```{r tables-model, results = "asis"}
table_outputconfig(model)
cat("\\begin{landscape}")
table_pars(model)
cat("\\end{landscape}")
table_likelihoods(model)
table_dq(model)
table_ts(model)
table_compweight(model)
```

<!-- ====================================================================== -->
<!-- 30model sensitivity tables -->
<!-- ====================================================================== -->
```{r tableretro, results = "asis"}
sa4ss::read_child(file.path(paste0(params$model, "_retro"), "mohnsrho.tex"))
```
\begin{landscape}
```{r tables-model-sens, results = "asis"}
table_sens(string_switchletter("../tables/sens_table_s_bio_rec.csv", params$area),
	       sens_group = "biology and recruitment")
table_sens(string_switchletter("../tables/sens_table_s_comp.csv", params$area),
	       sens_group = "composition data")
table_sens(string_switchletter("../tables/sens_table_s_index.csv", params$area),
           sens_group = "indices",
		   caption_extra = "The first sensitivity is an alternative recreational index. Other column names refer to index data that were taken out of the model.")
table_sens(string_switchletter("../tables/sens_table_s_sel.csv", params$area),
	       sens_group = "selectivity")
table_sens("../tables/table_compare_north_vs_south.csv",
	       caption = "Comparison of estimates of key parameters and derived quantities between the base model for north and south and the 2017 assessments for north and south. Note that the boundary between north and south differs between the current and 2017 assessments.")
```
\end{landscape}

```{r, results = 'asis'}
ignore <- table_projections(model)
cat(ignore)
```

```{r, results = "asis"}
decisiontable <- append(
  x = readLines(file.path("..", mod_loc, "decision_table.tex")),
  values = c("\\caption{\\label{tab:decision}Decision table summary of 10-year projections based on recent average catch for the first two years of the projection, alternative states of nature (columns), and management assumptions (asm.; rows) based on recent average catch and annual catch limits (ACLs) defined using an estimate of uncertainty (i.e., $P^*$) of 0.40 and 0.45. Catch and resulting fraction unfished are colored relatively with lighter colors representing lower values.}"),
  after = 1
)
cat(decisiontable)
```
