```{r selectivity-setupnotes, echo = FALSE, include = FALSE, eval = FALSE}
# get the block_breaks vector from this file:
knitr::purl("doc/model-selectivity.Rmd")
source("model-selectivity.R")
usethis::use_data(block_breaks_north, overwrite = TRUE)
usethis::use_data(block_breaks_south, overwrite = TRUE)
```

#### Selectivity and retention

Selectivity was modeled using the double-normal function of length
(option 24 in Stock Synthesis) with three of the six possible parameters estimated 
for each fleet.

The estimated parameters controlled the length at peak selectivity, the slope of the 
ascending limb and the slope of the descending limb (parameters 1, 3, and 4 in SS). 
The parameter controlling the width of the top was fixed at a small value (-15)
to make a smooth transition from ascending to descending with no flat top. 
Parameters 5 and 6 which control additional scaling of initial and final values
were not used (via the -999 code in SS).

Retention was modeled for the commercial trawl and commercial fixed-gear fleets
using a logistic function of length with 2 of the possible 4 parameters estimated.
The two estimated parameters controlled the length at 50\% retention and the 
slope of the ascending curve. Asymptotic retention was fixed at 100\% and no
sex-specific differences in retention were estimated.

Changes in selectivity and retention over time were modeled to account for 
management changes and gear changes. For changes in selectivity, all three 
estimated double-normal parameters were allowed to vary among time blocks 
as any change in the peak parameter will impact the shape associated with the 
other two. For changes in retention, the length at 50\% retention was allowed 
to vary over time, but the slope parameter was assumed to apply to all years
after the management measures were imposed in 1998.

Prior to 1998, all selected fish are assumed to be retained in the commercial
fisheries in keeping
with comments from those familiar with the history of the commercial fishery 
at the at the pre-assessment workshop and the Pikitch study in which 
more than 99\% of the observed `r spp` were retained
(pers. comm., J. Wallace, \gls{nwfsc}).

For commercial fisheries the assumed discard mortality rates are 
retained from the previous assessment: 50\% for trawl and 7\% for fixed gear. 

Selectivity for the recreational fisheries was modeled as representing
retained fish only and the retention process is represented within the 
assessment model only through time-varying selectivity that accounts
for changes in minimum size limits. 
A 7\% mortality rate has been assumed for lingcod
discarded in recreational fisheries and these dead discards
are accounted for in the total catch, but an exploratory analysis 
(Figure \@ref(fig:rec-selectivity-illustration)) indicated the the difference
between the expected length distributions with or without the dead 
discards included was small. Therefore, the length compositions
from recreational fisheries exclude all discards. Alternative approaches
to these assumptions were considered, but the available data do not support
them as it would "require 'unscrambling the egg' since B1 is a mixture of 
retained and discarded fish in the MRFSS data" 
(pers. comm., E.J. Dick, \gls{swfsc}).

The specific years with time blocks used for each fleet are noted below.

<!-- Commercial trawl -->
For commercial trawl, the time period of blocking on selectivity parameters 
were reduced from the the 2017 assessment, removing some blocks from the 
early years. The remaining points of change in selectivity were:

- 1993 (change in mesh size)
- 1998 (trip limits and size limits) 
- 2011 (implementation of the catch shares program)

Additionally, there were retention changes modeled in the following years,
retained from the 2017 assessment.

- 1998 (implementation of groundfish regulations)
- 2007 (groundfish regulations)
- 2010 (pre-catch share behavior change and clear reduction in discard rate)
- 2011 (implementation of the catch shares program)

All blocks were applied to the length at 50\% retention, but only the changes in
1998 and 2011 were applied to the parameter controlling the slope of the
retention function.

```{r} 
# create empty list
block_breaks <- list()

# first additions of blocks break points
block_breaks[["Comm_Trawl_sel"]] <- c(1993, 1998, 2011)
block_breaks[["Comm_Trawl_ret_infl"]] <- c(1998, 2007, 2010, 2011)
block_breaks[["Comm_Trawl_ret_width"]] <- c(1998, 2011)
```

<!-- Commercial fixed-gear -->
For commercial fixed-gear, selectivity was assumed to be constant
and retention was assumed to change in the following years:

- 1998 (implementation of groundfish regulations) 
- 2011 (implementation of the catch shares program)

The 2017 south model had a additional
blocks starting in 2002 and 2003 for the south model to account for closed areas. 
However, the composition data don't show evidence of a change around that time.

```{r} 
# add block break points to list created above
block_breaks[["Comm_Fix_ret_infl"]] <- c(1998, 2011)
block_breaks[["Comm_Fix_ret_width"]] <- c(1998, 2011)
```

<!--  recreational Washington (north model) -->
```{asis, opts.label = 'north'}

Changes in selectivity of the recreational WA fleet began in

- 1987 (management changes)
- 1995 (management changes)
- 1998 (first year of a series of management changes also made in 1999, 2000, 2001)
- 2007 (management changes)
- 2011 (management changes)
- 2017 (22" minimum size requirement was lifted from July 2017 to current 
for all catch areas but the change happened in the middle of the year)
```

```{r} 
# add block break points to list created above
block_breaks[["Rec_WA_sel"]] <- c(1987, 1995, 1998, 2007, 2011, 2017)
```

<!-- recreational Oregon -->
```{asis, opts.label = 'north'}
Changes in selectivity of the recreational OR fleet began in

- 1995 (the first year with a minimum size limit--22 inches)
- 1998 (min size limit was increased to 24 inches)
- 2007 (min size limit was reduced from 24 to 22 inches)

Not accounted for is a max size limit in place in Oregon for one year only
(2000) of 34 inches, which is visible in the data, but the absence of larger 
fish observed in a single year was assumed to have a negligible impact 
on the model results.
```

```{r} 
# add block break points to list created above
block_breaks[["Rec_OR_sel"]] <- c(1995, 1998, 2007)
```

<!-- recreational California -->
Changes in selectivity of the recreational CA fleet began in

```{asis, opts.label = 'north'}
- 1999 (min size limit 24 inches)
- 2011 (min size limit decreased to 22)

This represents a smaller number of blocks than used in the south model
which also included blocks starting in 1983 and 2017 as the data from 
northern California used in the north model are
sparser and correspond to a small fraction of the catch compared to the 
south model.
```
```{asis, opts.label = 'south'}
- 1983 (notable reduction in the number of small fish observed)
- 1999 (min size limit 24 inches)
- 2000 (min size limit increased to 26)
- 2002 (min size limit decreased to 24)
- 2011 (min size limit decreased to 22)
- 2017 (recreational fishery had access to deeper waters)

Not accounted for is a min size limit of 30 inches in 2004 as sample sizes
were low in that year.
```

```{r} 
# split breaks into separate north and south
block_breaks_north <- block_breaks
block_breaks_south <- block_breaks

# add block break points to list created above
block_breaks_north[["Rec_CA_sel"]] <- c(      1999,             2011)
block_breaks_south[["Rec_CA_sel"]] <- c(1983, 1999, 2000, 2002, 2011, 2017)
```

<!-- Triennial survey -->
A block on selectivity associated for the Triennial survey was explored
beginning 1995, the year associated with expanded 
spatial coverage and shift in timing, but not included in the 
base model.

```{r} 
# add block break points to list created above
# block_breaks[["Surv_TRI_sel"]] <- c(1995)
```
