#### Washington recreational index

```{r reccpuewa-setup, echo = FALSE, include = FALSE}
###############################################################################
# This file estimates the recreational CPUE for Washington
# with the code and write up embedded in a single file.
# Parameters will only be estimated if run_data == TRUE
#
# TO DO: A prioritized to do list, numbers are based on order of entry
#
# 2. move boattype, triptype, portgroup change to numeric code to
# recFIN package
# 4. reccpuewa-summarizedata -- Summarize the data prior to filtering
# 5. clean up the SM filter results in reccpuewa-filterSM
# 6. Think of filtering for filter_uppercpuequantile should come in when all
# other filtering is done rather than after SM
# 3. Make Mgmt based off of a lookup table rather than hard-coded so users can
# specify the table as an input parameter and then it will be created. This
# would largely be to document management regimes and not for a variable b/c
# the factor grouping doesn't work in the estimation code. Need to figure out
# if there is another way to include this in the model.
#
# DONE: A list of to do items that are finished
#
# 1. WA catches in CANADA, would be area == 20, which is already a filter
#
###############################################################################
# Set knitr options
run_data <- ifelse(exists("params"), params[["run_data"]], FALSE)
# knitr templates can be used in code chunks for consistent styles
knitr::opts_template$set(execute = list(
  eval = run_data,
  include = FALSE,
  echo = FALSE
))
```

```{r reccpuewa-objects}
#
# Response variable in the data set
colresponse <- sym(utils_name("Common"))
#
# SM filtering switch and percentage cutoff
filter_SM <- FALSE
filter_SM_cutoff <- 1.5
#
# Filter for extreme observations
# filter_upperquantile <- 0.975 # 2017 value that might be a relic of China.
filter_uppercpuequantile <- 0.999
#
# Regex of columns to remove
# Species that are not looked at or information on date that we do not need
removecolscalled <- "Week|Day|Shark|Tuna|Misc|Bird|Samp|SpeciesNotRecorded"
#
# Look up tables provided by T.T. that need to eventually be moved to recFIN
# with functions that change old information to new variable numbers
boattype <- data.frame(
  character = c("Charter", "Jetty", "Private"),
  numeric = 1:3
)
triptype <- data.frame(
  character = c(
    "BFO", "Dive", "Halibut", "Jig", "Other- Commercial",
    "Other- Non Fishing", "Salmon", "Tuna"
  ),
  numeric = c(
    6, 8, 1, 2, 4,
    4, 7, 3
  )
)
portgroup <- data.frame(
  character = c(
    "Westport", "LaPush", "Neah Bay", "Sekiu", "Johns River", "Chinook",
    "Ilwaco", "Hoquiam", "Tokeland", "Montesano", "Cosmopolis", "Columbia River Jetty"
  ),
  numeric = c(
    2, 3, 4, 5, 22, 31,
    11, 23, 24, 25, 26, 41
  )
)

# Read in the data
file_reccpuewadockside81 <- file.path("..", "data-raw", "Sport Dockside Interview_1981-1989.txt")
file_reccpuewadockside90 <- file.path("..", "data-raw", "Sport Dockside Interviews 1990-2016.txt")
file_reccpuewadockside17 <- file.path("..", "data-raw", "Sport Dockside Interviews 2017-2020.csv")
file_reccpuewaresults <- file.path("..", "data-raw", "reccpuewa-results.RData")
file_reccpuewafigures <- file.path("reccpuewa-figures.Rmd")
WA_dockside_dat_81_89 <- read.csv(file_reccpuewadockside81)
WA_dockside_dat_90_14 <- read.csv(file_reccpuewadockside90)
WA_dockside_dat_17_20 <- read.csv(file_reccpuewadockside17)
#
# data80s
#
reccpuewa_data1 <- WA_dockside_dat_81_89 %>%
  dplyr::rename(
    oldID = "InterviewID",
    Anglers = "AnglerAmount",
    GeneralRockfish = "General.Rockfish",
    Halibut = "Pacific.Halibut",
    Perch = "Pacific.Ocean.Perch"
  ) %>%
  dplyr::rename_with(
    .cols = tidyselect::everything(),
    ~ gsub("Interview|Group|\\.Rockfish|\\.", "", .x)
  ) %>%
  dplyr::rename_with(
    .cols = tidyselect::everything(),
    ~ gsub("Kept$", "", .x)
  ) %>%
  dplyr::select(-Date) %>%
  dplyr::mutate(
    Year = Year + 1900,
    TripType = triptype[match(TripType, triptype[["character"]]), "numeric"],
    BoatType = boattype[match(BoatType, boattype[["character"]]), "numeric"],
    Port = triptype[match(Port, portgroup[["character"]]), "numeric"]
  ) %>%
  dplyr::filter(!is.na(Anglers))
#
# data90s
#
# Create new columns, which are sum of retained and discard
reccpuewa_data2 <- WA_dockside_dat_90_14 %>%
  dplyr::select(-InterviewID) %>%
  dplyr::full_join(
  x = .,
  y = WA_dockside_dat_17_20,
  by = colnames(.)
  ) %>%
  dplyr::rename_with(~ gsub("BlackRock", "Black", .x)) %>%
  dplyr::rename_with(~ gsub("LingCod", "Lingcod", .x)) %>%
  dplyr::rename_with(~ gsub("Bocacciao", "Bocaccio", .x)) %>%
  dplyr::rename_with(~ gsub("Vermillion", "Vermilion", .x)) %>%
  dplyr::mutate(Area = dplyr::case_when(
    Area %in% c(74, 84) ~ 4,
    TRUE ~ Area
  )) %>%
  dplyr::mutate(ID = 1:NROW(.))
# Uncomment if you want total catch (discarded + retained; .tot) columns
# %>% dplyr::full_join(
#   suffix = c("", ".tot"),
#   by = "ID",
#   x = .,
#   y = dplyr::select(., -dplyr::matches(removecolscalled)) %>%
#     dplyr::select(-dplyr::matches("ID|Year|Port|Number|Type|Area|Angler|Depth|Month")) %>%
#     data.frame %>%
#     split.default(., f = gsub("Released$", "", names(.))) %>%
#     sapply(., FUN = rowSums, na.rm = TRUE) %>%
#     data.frame %>%
#     dplyr::mutate(ID = 1:NROW(.))
# ) %>%
# dplyr::select(-dplyr::matches("ID"))
#
# Combine data
#
reccpuewa_data <- dplyr:: full_join(
  x = reccpuewa_data2,
  y = reccpuewa_data1,
) %>% # End of combining data sets
  # Get rid of ID columns
  dplyr::select(-dplyr::matches("ID|Number")) %>%
  dplyr::select(-dplyr::matches(removecolscalled)) %>%
  # Add column for management regimes
  dplyr::mutate(
    # YearArea = paste0(Year, Area),
    CPUE_landed = {{colresponse}} / Anglers,
    Mgmt = dplyr::case_when(
      Year < 1987 ~ 1,
      Year %in% 1987:1994 ~ 2,
      Year %in% 1995:1997 ~ 3,
      Year == 1998 ~ 4,
      Year == 1999 ~ 5,
      Year == 2000 ~ 6,
      Year %in% 2001:2006 ~ 7,
      Year %in% 2007:2010 ~ 8,
      Year >= 2011 ~ 9
    )
  ) %>%
  # Rearrange columns
  dplyr::relocate(
    dplyr::matches("Year"),
    Month,
    Mgmt,
    Area, Port,
    TripType, BoatType, Anglers, Depth,
    CPUE_landed,
    dplyr::matches("Released")
  ) %>%
  dplyr::rename_with(
    .cols = tidyselect::everything(),
    ~ gsub("Released", ".Released", .x)
  )

# Filter
pretot <- reccpuewa_data %>%
  dplyr::mutate(tot = sum(Lingcod > 0, na.rm = TRUE)) %>%
  # Remove records without Angler information
  dplyr::filter(Anglers != 0) %>%
  # Remove records without Year information
  dplyr::filter(!is.na(Year)) %>%
  # Remove records without Area or BoatType information
  dplyr::filter(BoatType != "") %>%
  dplyr::filter(!is.na(Area)) %>%
  dplyr::mutate(
    `anncomplete info` = sum(Lingcod > 0, na.rm = TRUE),
    `bfncomplete info` = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)) %>%
  # Non-winter months
  dplyr::filter(Month %in% 4:8) %>%
  dplyr::mutate(
    annsummer = sum(Lingcod > 0, na.rm = TRUE),
    bfnsummer = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)
  ) %>%
  # Bottom fish only
  dplyr::filter(TripType == 6) %>%
  dplyr::mutate(
    `anngroundfish trip` = sum(Lingcod > 0, na.rm = TRUE),
    `bfngroundfish trip` = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)) %>%
  # Remove shore-based boats
  dplyr::filter(BoatType != 2) %>%
  dplyr::mutate(
    `annopen water` = sum(Lingcod > 0, na.rm = TRUE),
    `bfnopen water` = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)) %>%
  # Areas not specific to rockfish
  dplyr::filter(
    # Areas not specific to rockfish
    !(Area %in% c(0, 5, 6, 20, 41, 42, 51, 53:56, 61) &
      Year >= 1990
     )
  ) %>%
    # Areas not specific to rockfish
  dplyr::filter(
    # Areas not specific to rockfish
    !(Area %in% c(0, 5, 20, 42, 51, 55, 99) &
      Year < 1990
     )
  ) %>%
  dplyr::mutate(
    `annrockfish area` = sum(Lingcod > 0, na.rm = TRUE),
    `bfnrockfish area` = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)) %>%
  # Not enough records in area 52
  dplyr::mutate(
    `annremove area 52` = sum(Lingcod > 0, na.rm = TRUE),
    `bfnremove area 52` = sum(Lingcod > 0, na.rm = TRUE)/NROW(.)) %>%
  dplyr::filter(Area != 52) %>%
  # Remove colresponse with zero positive trips
  dplyr::select_if(colSums(., na.rm = TRUE) != 0)
reccpuewa_filtersummary <- dplyr::select(pretot, dplyr::matches("^ann|^bfn")) %>%
  dplyr::distinct() %>%
  tidyr::gather(key="ff", "value") %>%
  tidyr::separate(ff, sep = 3, into = c("type","Filter")) %>%
  tidyr::spread(key = c("type"), "value") %>%
  dplyr::arrange(bfn) %>%
  dplyr::mutate(bfn = bfn * 100) %>%
  dplyr::rename(`N pos.`= ann, `% pos.` = bfn) %>%
  dplyr::mutate(Description = c(
    "Remove records with missing information",
    "Keep April-August",
    "Remove all trips not targeting groundfish",
    "Remove shore-based fishing",
    "Remove area 52 because few samples",
    "Remove non-rockfish areas"
  )) %>%
  dplyr::relocate(Description, .after = Filter)
tot <- pretot %>%
  dplyr::select(-dplyr::matches("ann"), -dplyr::matches("bfn"))
tt <- knitr::kable(
  reccpuewa_filtersummary, booktabs = TRUE, longtable = TRUE, format = "latex",
  caption = paste("Data filtering steps to increase the percent positive (pos.) or number (N) of trips that landed", utils_name("common"), " in the Washington recreational index derived from dockside-sampling data."),
  label = "reccpuewa-filtersummary"
)
kableExtra::save_kable(x = tt,
  file = file.path("..", "tables", "reccpuewa-filtersummary.tex")
)
tt <- knitr::kable(
  tot %>% dplyr::group_by(Year) %>%
    dplyr::summarize(
      `N pos.` = sum({{colresponse}} > 0),
      `% pos.` = `N pos.` / dplyr::n() * 100, .groups = "keep"
    ),
    format = "latex", booktabs = TRUE, longtable = TRUE,
    caption = paste0("Number (N) of positive (pos.) samples and percent pos. per year",
      " of ", utils_name("common"), " in the Washington recreational dockside sampling program."),
    label = "reccpuewa-n"
)
kableExtra::save_kable(x = tt,
  file = file.path("..", "tables", "reccpuewa-n.tex")
)

# Table of n < 0, n > 0, is.na(n) for each species
# to determine which species should be used in the SM filtering
tablen <- tot %>%
  dplyr::select(Year, (dplyr::last(grep("\\.Re[a-z]+$", colnames(tot))) + 1):NCOL(tot)) %>%
  tidyr::gather(key = "colresponse", value = "n", -Year) %>%
  dplyr::group_by(colresponse) %>%
  dplyr::count(TF = n > 0) %>%
  tidyr::spread(key = "TF", value = "n") %>%
  dplyr::arrange(colresponse) %>%
  dplyr::group_by(colresponse) %>%
  dplyr::add_tally(`TRUE`, name = "sum_T") %>%
  dplyr::add_tally(`FALSE`, name = "sum_F") %>%
  dplyr::mutate_at(.vars = dplyr::vars(dplyr::matches("FALSE|TRUE|NA")), sum) %>%
  dplyr::mutate(prop = sum_T / (sum_T + sum_F) * 100) %>%
  dplyr::arrange(prop)
#
# Summary that was helpful while building
# tot %>% dplyr::group_by(Year) %>% dplyr::summarize_all(.f = function(x) all(is.na(x)))
# SM filtering
sppusedinSM <- tablen %>%
  dplyr::filter(prop >= filter_SM_cutoff, is.na(`<NA>`)) %>%
  dplyr::ungroup() %>%
  dplyr::filter_at(.vars = 1, ~ .x != as.character(colresponse)) %>%
  dplyr::pull(colresponse) %>% sort
sppformula <- paste(sppusedinSM, collapse = " + ") %>%
  paste(as.character(colresponse), "~", .) %>%
  as.formula
glm_SMresults <- stats::glm(
  formula = sppformula,
  family = stats::binomial(link = "logit"),
  data = as.data.frame(ifelse(tot > 0, 1, 0))
)
fishprob <- cbind(
  tot,
  prob = stats::predict(glm_SMresults, type = "response")
)
# Find min probability of occurring with target when target is landed
best.thresh <- sort(
  fishprob[["prob"]],
  decreasing = TRUE
)[sum(tot[[colresponse]] > 0)]
reccpuewa_SMcoefs <- data.frame(summary(glm_SMresults)$coef[, 1:2]) %>%
  dplyr::arrange(-Estimate) %>%
  dplyr::mutate(names = gsub("^X\\.", "", rownames(.)))
if (filter_SM) {
  reccpuewa_dataforEM <- fishprob[fishprob$prob>=best.thresh | fishprob[[colresponse]]>0,]
} else {
  reccpuewa_dataforEM <- fishprob
}

```
```{r todocleanthisup, echo = FALSE, include = FALSE, eval = FALSE}
###############################################################################
# clean up following code
#
# WRITE TWO DATA FRAMES: 
# 1) EQUAL NUMBER OF FALSE POSTIVES AND FALSE NEGATIVES
# 2) DROP ONLY THE 'TRUE NEGATIVES' (KEEP FALSE NEGATIVES... 'LOW PROBABILITY' TRIPS THAT STILL CAUGHT LINGCOD)
# BALANCE FALSE POSITIVES AND FALSE NEGATIVES
balanced_FPFN.df <- fishprob[fishprob$prob>=best.thresh,]
dim(balanced_FPFN.df)
length(which(balanced_FPFN.df[[colresponse]] >0))
summary(balanced_FPFN.df)
# write.table(balanced_FPFN.df, quote=F, row=F, sep=',', file="filtered_OR_ORBS_data_BALANCED_FP-FN.csv")
table(LingCaught=balanced_FPFN.df[[colresponse]]>0, KeepTrip=balanced_FPFN.df$prob>=best.thresh)
# look at the spatial and temporal distribution of samples
with(balanced_FPFN.df, table(Year,Port))
#print("Filtered data set saved as 'filtered_OR_ORBS_data_BALANCED_FP-FN.csv'")
# DROP ONLY TRUE NEGATIVES
# keep all trips with prob >= best.thresh ***OR*** with positive Lingcod catch (correct habitat, by def'n)
# write.table(reccpuewa_dataforEM, quote=F, row=F, sep=',', file="filtered_OR_ORBS_data_DROP_ONLY_TRUE_NEGS.csv")
table(LingCaught=reccpuewa_dataforEM[[colresponse]]>0, KeepTrip=reccpuewa_dataforEM$prob>=best.thresh)
# look at the spatial and temporal distribution of samples
with(reccpuewa_dataforEM, table(Year,Port))
```
```{r reccpuewa-mle}
reccpuewa_dataforEM$Year <- factor(reccpuewa_dataforEM$Year)
reccpuewa_dataforEM$Month <- factor(reccpuewa_dataforEM$Month)
reccpuewa_dataforEM$BoatType <- factor(reccpuewa_dataforEM$BoatType)
reccpuewa_dataforEM$TripType <- factor(reccpuewa_dataforEM$TripType)
reccpuewa_dataforEM$Area <- factor(reccpuewa_dataforEM$Area)
reccpuewa_dataforEM[["tgt.sp.pa"]] <- as.numeric(reccpuewa_dataforEM[[colresponse]] > 0)
reccpuewa_dataforEM[["cpue"]] <- reccpuewa_dataforEM[["CPUE_landed"]]
#
# drop records with catch rates above the 99.9 percentile
# ADW - changed this to 97.5 percentile after the best positive model below indicated 
# significant outliers
reccpuewa_dataforEM <- subset(
  reccpuewa_dataforEM,
  reccpuewa_dataforEM[[colresponse]] / reccpuewa_dataforEM[["Anglers"]] <=
  quantile(reccpuewa_dataforEM[[colresponse]] / reccpuewa_dataforEM[["Anglers"]], probs = filter_uppercpuequantile)
)
reccpuewa_dataforEM <- droplevels(reccpuewa_dataforEM)
```
```{r reccpuewa-models, opts.label = 'execute'}
mod_b <- glm(tgt.sp.pa ~ Year + BoatType + Area + Month, family=binomial,data=reccpuewa_dataforEM)
mod_l_lognormal <- glm(log(cpue) ~ Year + BoatType + Area + Month, data=reccpuewa_dataforEM[reccpuewa_dataforEM[[colresponse]] > 0, ])
mod_l <- glm(cpue ~ Year + BoatType + Area + Month, data=reccpuewa_dataforEM[reccpuewa_dataforEM[[colresponse]] > 0, ], family = Gamma(link="log"))
# summary(mod_b)
# summary(mod_l)
# anova(mod_b, test="Chi")
# anova(mod_l, test="Chi")
best_bin.glm_STAN <- rstanarm::stan_glm(
  formula = tgt.sp.pa ~ Year + BoatType + Area + Month,
  family = binomial, data = reccpuewa_dataforEM,
  prior = rstanarm::normal(),
  iter = 10000, cores = 3
)
best_pos.glm_STAN <- rstanarm::stan_glm(
  formula = cpue ~ Year + BoatType + Area + Month,
  family = Gamma(link = "log"), data = reccpuewa_dataforEM[reccpuewa_dataforEM[[colresponse]] > 0, ],
  prior = rstanarm::normal(location = 0, scale = 10),
  prior_intercept = rstanarm::normal(location = 0, scale = 10),
  iter = 10000, cores = 3
)
lognormal_pos.glm_STAN <- rstanarm::stan_glm(
  formula = log(cpue) ~ Year + BoatType + Area + Month,
  family = gaussian, data = reccpuewa_dataforEM[reccpuewa_dataforEM[[colresponse]] > 0, ],
  prior = rstanarm::normal(location = 0, scale = 10),
  prior_intercept = rstanarm::normal(location = 0, scale = 10),
  iter = 10000, cores = 3
)
save(
  mod_b, mod_l, mod_l_lognormal,
  # lognormal_pos.glm_STAN,
  best_bin.glm_STAN, best_pos.glm_STAN,
  file = file_reccpuewaresults
)
```
```{r reccpuewa-stanresults, eval = !run_data}
# Read in the results if run_data == FALSE
load(file_reccpuewaresults)
```

```{r reccpuewa-index, echo = FALSE, warnings = FALSE}
pred_bin<- exp(coef_year(mod_b))/(1+exp(coef_year(mod_b)))
var_pos <- diag(vcov(mod_l))[1:length(pred_bin)]
pred_pos <- exp(coef_year(mod_l) + (var_pos / 2))
index_mle <- pred_bin * pred_pos
combine <- (
  exp(coef_year(best_bin.glm_STAN)) /
  (1 + exp(coef_year(best_bin.glm_STAN)))
) * exp(coef_year(best_pos.glm_STAN))
index_MCMC <- cbind.data.frame(
  year = as.numeric(names(combine)),
  obs = apply(combine, 2, median),
  # obs = apply(combine,2,mean) + (apply(combine,2,var)/2),
  se_log = apply(log(combine),2,sd),
  seas = 7,
  index = get_fleet(value = "WA", area = "north", col = "num"),
  area = "north",
  HPD_lower = apply(combine,2,quantile, probs=c(0.025)),
  HPD_upper = apply(combine,2,quantile, probs=c(0.975))
)
utils::write.csv(index_MCMC,
  row.names = FALSE,
  file = file.path("..", "data-raw", "reccpuewa.csv")
)
tt <- kableExtra::kbl(
  index_MCMC %>%
    dplyr::select(year, obs, se_log, HPD_lower, HPD_upper) %>%
    dplyr::mutate_at(vars(-year),round,2) %>%
    dplyr::rename(Year = year, Mean = obs, logSE = se_log,
           `lower HPD` = HPD_lower, 
           `upper HPD` = HPD_upper),
  booktabs = TRUE,
  label = "reccpuewa-results",
  caption = paste0("Standardized index for the ", paste0(params$area, "ern area "), 
                  "survey index with log-scale standard errors (SEs) and 95 percent highest posterior density (HPD) intervals for ",
                  utils_name("common"),"."),
  row.names = F) %>% 
  kableExtra::kable_styling(latex_options = "striped")
kableExtra::save_kable(tt,
  file = file.path("..", "tables", "reccpuewa-results.tex")
)

# Make figures
gg <- ggplot2::ggplot(
  reccpuewa_SMcoefs %>% dplyr::mutate(names = factor(names, levels = names[order(Estimate)])) %>% 
  dplyr::filter(!grepl("Intercept", names)),
  ggplot2::aes(
    x = factor(names),
    y = Estimate
  )
) +
  ggplot2::geom_bar(position = ggplot2::position_dodge(), stat = "identity", fill = "blue") +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = Estimate - 1.96 * Std..Error,
      ymax = Estimate + 1.96 * Std..Error
    ),
    width = 0.6, # Width of the error bars
    position = ggplot2::position_dodge(0.9)) +
    ggplot2::labs(
      x = "Species",
      y = paste0("Estimated co-occurrence with ", utils_name("common"))
    ) +
    ggplot2::coord_flip() +
    ggplot2::theme_bw()
ignore <- ggsave2(
  gg,
  filename = file.path("..", "figures", "reccpuewa-filterSMcoef.png"),
  caption = paste0(
    "Estimates of species coefficients (blue bars) from the ",
    "binomial generalized linear model (GLM) ",
    "for presence/absence of ",
    utils_name("common"),
    " in the Washington recreational dockside interview data. ",
    "Horizontal black bars represent the 95\\% confidence intervals."
  ),
  alttext = paste0(
    reccpuewa_SMcoefs[1, "names"], " and ",
    tolower(dplyr::last(reccpuewa_SMcoefs[["names"]])),
    " are the most and least likely species to co-occur with ",
    utils_name("common"), " in the Washington recreational fishery."
  ),
  label = "reccpuewa-filterSMcoef"
)
#
#
#
```
```{r reccpuewafigures, echo = FALSE, include = FALSE}
grDevices::png(
  filename = file.path("..", "figures", "reccpuewa-ScaledQQplot_bin.png"),
  width = 6, height = 3, units = "in", res = 300, pointsize=6
)
p_res <- DHARMa::simulateResiduals(fittedModel = mod_l, n = 500,integerResponse = T) # had to reduce n in order to run, hitting memory limit
plot(p_res, rank=TRUE, quantreg=TRUE)
grDevices::dev.off()
grDevices::png(
  filename = file.path("..", "figures", "reccpuewa-ScaledQQplot_pos.png"),
  width = 6, height = 3, units = "in", res = 300, pointsize=6
)
p_res <- DHARMa::simulateResiduals(fittedModel = mod_b, n = 500,integerResponse = T) # had to reduce n in order to run, hitting memory limit
plot(p_res, rank=TRUE, quantreg=TRUE)
grDevices::dev.off()

# write an ordered csv file to be called in later
utils::write.csv(
  row.names = FALSE,
  lapply(
    file.path("..", "figures", c("reccpuewa-filterSMcoef.csv")),
    utils::read.csv
  ) %>% dplyr::bind_rows(., .id = "id") %>% dplyr::select(-id) %>%
  dplyr::full_join(., by = c("caption", "alt_caption", "label", "filein"),
  data.frame(
    caption = c(
      "Scaled quantile-quantile (QQ) plot (left panel) and rank-transformed versus standardized residuals (right panel) for the binomial model of the Washington recreational index.",
      "Scaled quantile-quantile (QQ) plot (left panel) and rank-transformed versus standardized residuals (right panel) for the positive model of the Washington recreational index."
    ),
    alt_caption = c(
      "Diagnostic tests reveal one to one relationship between expected and observed residuals.",
      "Diagnostic tests reveal one to one relationship between expected and observed residuals."
    ),
    label = c(
      "reccpuewa-mleqqscaledbin",
      "reccpuewa-mleqqscaledpos"
    ),
    filein = c(
      file.path("..", "figures", "reccpuewa-ScaledQQplot_bin.png"),
     file.path("..", "figures", "reccpuewa-ScaledQQplot_pos.png")
   )
  )
),
  file = file.path("..", "figures", "reccpuewa.csv")
)

#
#
#
# gg <- ggplot2::ggplot(
#   data = as.data.frame(
#     cbind(Median = coef(best_bin.glm_STAN), 
#       coef(mod_b))),
#   ggplot2::aes(V2, Median)
# ) +
# ggplot2::geom_point(pch = 1, cex = 2) +
# ggplot2::geom_point(
#   data = as.data.frame(cbind(Median = coef(best_pos.glm_STAN), coef(mod_l))),
#   pch = 19, cex = 2
# ) +
# ggplot2::geom_abline(intercept = 0, slope = 1) +
# ggplot2::labs(
#   x = "Maximum likelihood estimates of GLM parameters",
#   y = "Median posterior GLM parameters"
# ) +
# ggplot2::theme_bw()
# ignore <- ggsave2(
#   gg,
#   filename = file.path("..", "figures", "reccpuewa-mlevbayesian.png"),
#   caption = paste0(
#     "Comparison of estimates of the delta generalized linear model (GLM) ",
#     "estimated using a maximum likelihood framework (x axis) and ",
#     "Bayesian framework (y axis) for the binomial model (open circles) and ",
#     "the positive model (closed circles) to a perfect relationship ",
#     "(i.e., 1:1; solid line)."
#   ),
#   alttext = paste0(
#     "Estimates fall on the one-to-one line for both models."
#   ),
#   label = "reccpuewa-mlevbayesian"
# )
#
#
#
# ggplot2::ggplot(index_MCMC, ggplot2::aes(year, obs)) +
# ggplot2::geom_line(col = "black", size = 2) +
# ggplot2::geom_ribbon(ggplot2::aes(ymin = HPD_lower, ymax = HPD_upper)) +
# ggplot2::geom_line(col = "gray", size = 1,
#   data = data.frame(year = as.numeric(names(index_mle)), obs = index_mle)
# ) +
# ggplot2::labs(x = "Year", y = "Estimated index (todo units here)") +
# Previous estimates errors out
# ggplot2::geom_line(data = old, col = "red")
#
#
#
# plot(stats::fitted(best_pos.glm_STAN),log(reccpuewa_dataforEM[reccpuewa_dataforEM[[colresponse]] > 0, "cpue"]),xlim=c(-5,2),ylim=c(-5,2),xlab="Expected value",ylab="ln(CPUE)")
# lines(-5:5,-5:5)
# plot(stats::fitted(best_pos.glm_STAN),resid(best_pos.glm_STAN),pch=20,cex=0.8,abline(0,0))
# qqnorm(stats::resid(best_pos.glm_STAN),xlab="Quantiles of standard normal distribution",ylab="Residuals",xlim=c(-4,4),ylim=c(-4,4))
# abline(0,1)
# plot(fitted(best_pos.glm_STAN),sqrt(abs(resid(best_pos.glm_STAN))))
# plot(best_pos.glm_STAN)
```

The Washington dockside sampling program (Ocean Sampling Program
and Puget Sound Baseline Sampling Program) is supported by
\gls{wdfw} and collects biological as well as catch data.
The coastal portion of this program is largely sampled at three major ports,
Westport, La Push, and Neah Bay. `r Spp` are one of three rockfish
species that are highly targeting by recreational fishers, and thus,
have been recorded to the species level since the beginning of the program.

Information on retained `r utils_name()` from dockside interviews
were available from \gls{wdfw} between
`r knitr::combine_words(range(data_index_cpue[data_index_cpue[["index"]] == get_fleet("WA", col = "num"), "year"]))`.
Recent data also included information on discarded fish,
but this information was not used for this analysis because
(1) it was not available for the entire time series and
(2) the composition data that are associated with this index only include retained fish.
Information from dockside interviews are thought to be more reliable than
information contained in the \gls{mrfss} database, and thus, \gls{mrfss}
data were not explored with respect to Washington recreational \gls{cpue}.

The dockside data were filtered prior to being fit to models to
identify the best subset of the available data that are likely to be
consistent over the time series and provide a reliable index of abundance
once standardized (Table \@ref(tab:reccpuewa_filtersummary)).
Depth was not recorded for the entire time period, and thus was not included
as a filter or a subsequent covariate.
The filtering procedure led to a final positive rate of
`r sprintf("%.2f", max(reccpuewa_filtersummary[["% pos."]]))`\%.

Stephens-MacCall [-@stephens2004] filtering approach was explored to
predict the probability of catching `r utils_name("common")` based on
the species composition of the sampler-observed catch in a given trip.
Prior to applying the Stephens-MacCall filter, we identified potentially
informative predictor species, i.e., species with sufficient sample sizes and
temporal coverage (at least `r filter_SM_cutoff` \% of all trips)
to inform the binomial \gls{glm} used in the Stephens-MacCall approach.
Thus, the remaining species all co-occurred with
`r utils_name("common")` in at least one trip
and were retained for the Stephens-MacCall logistic regression.
Estimated coefficients from the Stephens-MacCall analysis are
positive for species that are likely to co-occur with the target species and
negative for species that are likely to not co-occur with the target species.
The top five species with high probability of
co-occurrence with `r spp` included
`r knitr::combine_words(tolower(names(sort(coef(glm_SMresults),decreasing=TRUE)[1:5])))`
(Figure \@ref(fig:reccpuewa-filterSMcoef)),
all of which are associated with rocky reef and kelp habitats.
The species with the lowest probability of co-occurrence with `r spp` was
`r knitr::combine_words(tolower(names(sort(coef(glm_SMresults),decreasing=FALSE)[1])))`.
Given the high positivity rate of `r spp` prior to the Stephens-MacCall filtering
(Table \@ref(tab:reccpuewa-n)),
we choose to not use this additional filtering process.

The filtered data were used to fit Bayesian delta-\glspl{glm} using the
same modelling framework, rstanarm [@rstanarm2020], as the other \gls{cpue} indices developed
for `r spp`.
Covariates considered included year, boat type, area, and month.
A management covariate was investigated previously, but the framework cannot estimate
both fixed effects for year and groups of years.
A full model with all covariates was fit and goodness of fit was tested using
Chi-square goodness of fit test, that indicated a model with all variables
fit the data the best. This process was repeated for several distributional
assumptions for the positive component and
posterior predictive checks of the Bayesian model fit for all models
regardless of the distributional assumptions used to fit the data were similar
(results not shown).
The Gamma distribution was chosen going forward given a better match of the
theoretical quantiles to the data quantiles than the lognormal
(Figures \@ref(fig:reccpuewa-mleqqscaledbin) and \@ref(fig:reccpuewa-mleqqscaledpos)).

The terminal year of the index was poorly estimated and indicated a sharp increase
in the abundance of the stock. This sharp increase in the terminal year is not
new and was present in the last standardization of this data set.
