---
title: "Lingcod"
author: "Lingcod STAT"
date: "July 12, 2021"
fig.caption: TRUE
output: 
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    yolo: false
    self_contained: true
    lib_dir: libs
    chakra: libs/remark-latest.min.js
    nature:
      highlightStyle: tomorrow-night-bright
      highlightLines: true
      highlightLanguage: r
    css: ["ninjutsu", xaringan-themer.css, libs/animate.css]
    seal: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  message = FALSE,
#   dev = "svg",
  fig.width = 12,
  fig.height = 12
  # fig.retina = 3
  )
xaringanthemer::style_mono_accent(
  # base_color = nmfspalette::nmfs_cols("darkblue"),
  base_color = "#00467F",
  header_font_google = xaringanthemer::google_font("Josefin Sans"),
  text_font_google   = xaringanthemer::google_font("Montserrat", "300", "300i"),
  code_font_google   = xaringanthemer::google_font("Fira Mono")
)
```

class: title-slide, inverse
```{css}
<style>
.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}
</style>
```
```{css}
.code-bg-white .remark-code, .code-bg-white .remark-code * {
 background-color:white!important;
}
```

.bg-text[
# Lingcod catches and other data
<hr />
Lingcod STAT<br><br>
July 12, 2021<br>
]

---
class: top

## Fleet structure

Change splitting of data from
42 $^{\circ}$ 00' N to
40 $^{\circ}$ 10' N.

.pull-left[

### 2019

* North
  * Commercial
     * Fixed gear
     * Trawl
  * Recreational
     * Washington
     * Oregon
* South
  * Commercial
     * Fixed gear
     * Trawl
  * Recreational
     * California
]
.pull-right[

### 2021

* North
  * Commercial
     * Fixed gear
     * Trawl
  * Recreational
     * Washington
     * Oregon
     * Northern California
* South
  * Commercial
     * Fixed gear
     * Trawl
  * Recreational
     * Southern California
]

???
* Kept OR and CA recreational data as separate fleets because of differences in management

---
class: split-20

.column.bg-blue[
#### .white[2021 landings]

.white[
* North
* South
]
]

.column.bg-white[
```{r catch2-landings-stacked-north, results = "asis"}
sa4ss::add_figure(
  width = 80,
  file.path("..", "docs", "North", "catch2 landings stacked.png"),
  caption = ""
)
sa4ss::add_figure(
  width = 80,
  file.path("..", "docs", "South", "catch2 landings stacked.png"),
  caption = ""
)
```
]

---
```{r, results = "asis"}

```










---
### Extra slides

---
class: split-20

.column.bg-blue[
#### .white[Commercial landings]
]

.column.bg-white[
```{r catch-comm-state, results = "asis"}
do.call(sa4ss::add_figure, c(width = 100, height = 90,utils::read.csv((file.path("..", "figures", "catch-comm-state.csv")))))
```
]

???
* Previously, a linear interpolation of reconstructed catches in California
* Management measures in 1998 which led to decreased catches