---
title: 'Status of Lingcod (South) stock off the U.S. West Coast in 2027'
author:
  - name: 'Ian Taylor'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Sabrina Beyer'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Chantel Wetzel'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Megan Feddern'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Melissa Monk'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
date: today
keep-tex: true 
tbl-pos: 't' 
echo: false 
cover: support_files/Lingcod_(South).png
pdf-engine: lualatex
format: 
  pdf: 
    documentclass: article
    papersize: letter
    number-sections: true
    template-partials:
      - 'support_files/before-body.tex'
      - 'support_files/_titlepage.tex'
    include-in-header:
      - 'support_files/in-header.tex'
    toc: true
    lof: true
    lot: true
    titlepage-geometry: 
      - top=2in
      - bottom=1in
      - right=1in
      - left=1in
output-file: 'Lingcod_(South)_SAR_2027' 
params:
   office: '\gls{nwfsc}'
   species: 'Lingcod (South)'
   spp_latin: 'Ophiodon elongatus'
   region: 'U.S. West Coast'
bibliography:  
  - bibliography_files/aquaculture.bib
  - bibliography_files/asar_citation.bib
  - bibliography_files/canjfishaquatsci.bib
  - bibliography_files/conservation-policy-management.bib
  - bibliography_files/ecology.bib
  - bibliography_files/fish.bib
  - bibliography_files/fishres.bib
  - bibliography_files/icesjmarsci.bib
  - bibliography_files/jfishbiol.bib
  - bibliography_files/oceanography-limnology.bib
  - bibliography_files/transamfishsoc.bib
csl: support_files/cjfas.csl
---
\printnoidxglossaries 

```{r} 
#| label: 'R_parameters'
#| warnings: false 
#| eval: true
# Parameters 
spp <- params$species 
SPP <- params$species 
species <- params$species 
spp_latin <- params$spp_latin 
office <- params$office
region <- params$region
``` 

```{r} 
#| label: 'preamble'
#| warning: false 
#| eval: true 
#| include: false
# load converted output from stockplotr::convert_output() 
load("../doc/report_south/lingcod_output.rda") 
# Call reference points and quantities below 
output <- out_new |> 
  dplyr::mutate(estimate = as.numeric(estimate), 
    uncertainty = as.numeric(uncertainty)) 
source("preamble.R") 
# Available quantities
start_year
end_year
Fend # terminal fishing mortality
Ftarg # fishing mortality at msy
F_Ftarg # Terminal year F respective to F target
Bend # terminal year biomass
Btarg # target biomass (msy)
total_catch # total catch in the last year
total_landings # total landings in the last year
SBend # spawning biomass in the last year
M # overall natural mortality or at age
Bmsy # target spawning biomass(msy)
h # steepness
R0 # recruitment

``` 

{{< pagebreak >}}

## Disclaimer {.unnumbered .unlisted}

These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited or reproduced. They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce.

{{< pagebreak >}} 

Please cite this publication as: 

Taylor, I., Beyer, S., Wetzel, C., Feddern, M., and Monk, M. 2027. Status of Lingcod (South) stock off the U.S. West Coast in 2027. Pacific Fishery Management Council, Portland, OR. \pageref*{LastPage}{} pp. Available from https://www.pcouncil.org/stock-assessments-and-fishery-evaluation-safe-documents/

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'executive_summary'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01_executive_summary.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'introduction'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('02_introduction.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'data'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('03_data.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-configuration'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04a_assessment-configuration.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-results'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04b_assessment-results.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-sensitivity'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04c_assessment-sensitivity.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-benchmarks'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04d_assessment-benchmarks.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-projections'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04e_assessment-projections.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'discussion'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('05_discussion.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'acknowledgments'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('06_acknowledgments.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'references'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('07_references.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'figures'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('08_figures.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'tables'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('09_tables.qmd', quiet = TRUE)
cat(a, sep = '\n')
# Force LaTeX to render all floating tables before moving to the next section
cat('\n\\clearpage\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'appendix'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('11_appendix.qmd', quiet = TRUE)
cat(a, sep = '\n')
```
